Augraphy: A Data Augmentation Library for Document Images

### 2023-04-30 paper.tex

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoised}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.

@@

\section{Conclusion and Future Work}
We presented \emph{Augraphy}, a framework for generating realistic synthetically-augmented datasets of document images.
Other available image augmentation tools were examined and found to lack features needed for our purposes, motivating the creation of this library specifically targeting the types of alterations and degradations seen in document images.

We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional NAFNet instance on this corpus.

@@

Future work on the \emph{Augraphy} library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets on commodity hardware, providing more scale-invariant support so that augmentations perform well at all document image resolutions, and responding to community-initiated feature requests.

\emph{Augraphy} is licensed under the MIT open source license, and readers are invited to share feedback and participate in its development on GitHub.

>>>>

\begin{samepage}
\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoised}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.
\end{samepage}

@@

\section{Conclusion and Future Work}
We presented \emph{Augraphy}, a framework licensed under the MIT open source license for generating realistic synthetically-augmented datasets of document images.
Other available tools were examined and found to lack needed features, motivating the creation of this library specifically supporting alterations and degradations seen in document images.

We described how to use \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional NAFNet instance on this corpus.

@@

Future work on the \emph{Augraphy} library will focus on adding new types of augmentations, increasing performance to enable faster creation of larger datasets, providing more scale-invariant support for all document image resolutions, and responding to community-initiated feature requests.
